Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle structure

### 2017-06-12 documents/TriangleScenarioArXiv/ts.tex
pre-injectable -> ai-expressible

    Not all sets $N' \subseteq \nodes'$ can be written as the disjoint union of injectable sets, but those that \textit{can} are called the \term{pre-injectable sets} of $\graph'$. A set $N' \subseteq \nodes'$ is a pre-injectable set if it can be decomposed into the disjoint union of injectable sets $N' = \coprod_{i} N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ and all pairs $N_i', N_j'$ are ancestrally independent: $\forall i, j : N_i' \ancestralindep N_j'$.

    A pre-injectable set $N'$ is of primal importance to the Inflation Technique because any distribution over $N'$ will factorize according to its ancestral independence conditions~\cite{Pearl_2009}\footnote{In~\cite{Inflation}, this concept is generalized into terms which can be factorized via d-separation conditions and the corresponding inflated sets are termed \textit{expressible sets}. This generalization was not required for this work in particular because the ancestral independence relations formed a generating set of d-separation conditions for all of the inflations considered in \cref{fig:inflations}.},
    \[ \prob[N'] = \prob[\coprod_i N'_i] = \prod_{i}\prob[N'_i] \]
    Application of the inflation lemma to linear inequalities constraining pre-injectable distributions $\prob[N']$ transforms those inequalities into polynomial inequalities over the injectable distributions, allowing one to replace all terms with probability distributions defined over variables in $\nodes$. Throughout the body of this work, we let $\PreInj[\graph]{\graph'}$ denote the set of all pre-injectable sets. To derive inequalities for the inflated causal structure $\graph'$, the pre-injectable sets define a marginal scenario $\mscenario$\footnote{Analogously for a marginal scenario $\mscenario$, the pre-injectable sets $\PreInj[\graph]{\graph'}$ form an \textit{abstract simplicial complex}. Therefore, in practice, it is completely sufficient to focus on the maximal pre-injectable sets.} that are used to derive inequalities using methods discussed in \cref{sec:marginal_satisfiability}.

@@

    \Cref{sec:inflation_technique_main_summary} explains how the Inflation Technique~\cite{Inflation} was used to derive novel causal compatibility inequalities for the Triangle structure by constructing inflations of the Triangle structure satisfying \cref{eq:inflation_defn}. Explicitly, for a given inflation $\graph'$ of the Triangle structure, one constructs a marginal problem (see \cref{sec:marginal_satisfiability}) for the marginal scenario $\mscenario$ composed of the maximal pre-injectable sets of $\graph'$, i.e. $\mscenario = \PreInj[\graph]{\graph'}$. This section acts as a reference for the particular inflations of the Triangle structure that are mentioned throughout this manuscript. Contained within this section is a depiction of each of these inflations in \cref{fig:inflations} as well as a their pre-injectable sets. An efficient algorithm for computing the injectable and pre-injectable sets of an inflation can be found in~\cite{Inflation}.
    \begin{center}
    \begin{figure}
    \begin{subfigure}[b]{.45\linewidth}
    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure_cut}}
    \caption{The Cut inflation.}\label{fig:cut_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.45\linewidth}
    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral}}
    \caption{The Spiral inflation.}\label{fig:spiral_inflation}
    \end{subfigure}

@@

    The first inequality presented in \cref{sec:found_inequalities} was \cref{eq:ww_ineq}. \cref{eq:ww_ineq} was derived using the Wagon-Wheel inflation in \cref{fig:wagon_wheel_inflation}. The Wagon-Wheel inflation possesses $4$ copies of $C$ ($C_1, C_2, C_3, C_4$) and $2$ copies of $A$ ($A_1, A_2$) and $B$ ($B_1, B_2$) arranged in the shape of a Wagon-Wheel. The maximal pre-injectable sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{eq:pre_injectable_triangle_structure_wagon_wheel}. These maximal pre-injectable sets define the following marginal scenario where the joint variables $\jointvar$ are simply the set of observable nodes in the Wagon-Wheel inflation $\jointvar = \nodes'_O$:
    \[ \mscenario = \PreInj[\graph]{\graph'} = \bc{\bc{A_2, B_1, C_3, C_1}, \bc{A_1, B_1, C_4, C_2}, \bc{A_1, B_2, C_1, C_3}, \bc{A_2, B_2, C_2, C_4}} \eq \label{eq:wagon_wheel_marginal_model}\]
    Given that the Fritz distribution is defined over $4$-outcomes variables, the variables in the marginal scenario are assigned $4$-outcomes as well. This marginal scenario $\mscenario$ then defines an incidence matrix $M$ capable of accommodating the Fritz distribution that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{4} = 1024$ rows and $\abs{\Events{\jointvar}} = 4^8 = 65,536$ columns. Understandably, this matrix is not reproduced here. The sheer size of the incidence matrix used here makes complete solutions of the marginal problem using tools such as linear-quantifier elimination intractable.

    \begin{equation*}
        \eq \label{eq:pre_injectable_triangle_structure_wagon_wheel}
        \begin{gathered}
            \textbf{Maximal Pre-injectable Sets} \\
            \bc{A_2, B_1, C_3, C_1} \\
            \bc{A_1, B_1, C_4, C_2} \\
            \bc{A_1, B_2, C_1, C_3} \\
            \bc{A_2, B_2, C_2, C_4} \\
        \end{gathered}
        \qquad
        \begin{gathered}
            \textbf{Ancestral Independences} \\
            \bc{A_2, B_1, C_3} \ancestralindep \bc{C_1} \\
            \bc{A_1, B_1, C_4} \ancestralindep \bc{C_2} \\
            \bc{A_1, B_2, C_1} \ancestralindep \bc{C_3} \\
            \bc{A_2, B_2, C_2} \ancestralindep \bc{C_4} \\
        \end{gathered}
    \end{equation*}
    To construct the marginal distribution vector $\probvec^{\mscenario}$ for the Fritz distribution, one begins with $\probvec^{\mscenario}$ defined in a \textit{symbolic} form,
    \[ {\probvec^{\mscenario}}^{\intercal} = \underbrace{\br{\prob[A_2B_1C_3C_1]\br{0000}, \ldots, \prob[A_1B_1C_4C_2]\br{3232}, \ldots, \prob[A_2B_2C_2C_4]\br{3333}}}_{1024 \text{ entries}} \eq \label{eq:marginal_vector_wagon_wheel} \]
    Which can be factored into the ancestrally independent injectable sets using \cref{eq:pre_injectable_triangle_structure_wagon_wheel},
    \[ {\probvec^{\mscenario}}^{\intercal} = \br{\prob[A_2B_1C_3]\br{000}\prob[C_1]\br{0}, \ldots, \prob[A_1B_1C_4]\br{323}\prob[C_2]\br{2}, \ldots, \prob[A_2B_2C_2]\br{333}\prob[C_4]\br{3}} \eq \label{eq:marginal_vector_wagon_wheel_factors}\]
    And penultimately, each probability distribution in \cref{eq:marginal_vector_wagon_wheel_factors} is deflated by dropping copy-indices.
    \[ {\probvec^{\mscenario}}^{\intercal} = \br{\prob[ABC]\br{000}\prob[C]\br{0}, \ldots, \prob[ABC]\br{323}\prob[C]\br{2}, \ldots, \prob[ABC]\br{333}\prob[C]\br{3}} \eq \label{eq:marginal_vector_wagon_wheel_factors_dropped}\]
    This step is permitted because all of the remaining distributions in \cref{eq:marginal_vector_wagon_wheel_factors} are defined over the injectable sets of the Wagon-Wheel inflation. Finally, each of the elements of $\probvec^{\mscenario}$ are replaced with numerical values pursuant to the Fritz distribution. For example, $\prob[ABC]\br{323}\prob[C]\br{2}$ is assigned the following numerical value:
    \[ \prob[ABC]\br{323}\prob[C]\br{2} = \f{1}{32}\br{2 + \sqrt{2}} \cdot \f{1}{4} \simeq 0.0267  \]
    The same is applied to all other entries of $\probvec^{\mscenario}$. Finally, this numerical version of $\probvec^{\mscenario}$ and $M$ are subjected to linear programing software and an infeasibility certificate $y$ was obtained, corresponding precisely to \cref{eq:ww_ineq} using \cref{eq:marginal_vector_wagon_wheel_factors_dropped}.

    The remaining inequalities in \cref{sec:found_inequalities} were derived using the Web inflation of \cref{fig:the_web_inflation}. The maximal pre-injectable sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{eq:pre_injectable_triangle_structure_web}.
    \begin{equation*}
        \eq \label{eq:pre_injectable_triangle_structure_web}
        \begin{gathered}
            \textbf{Maximal Pre-injectable Sets} \\
            \bc{A_1, B_1, C_1, A_4, B_4, C_4} \\
            \bc{A_1, B_2, C_3, A_4, B_3, C_2} \\
            \bc{A_2, B_3, C_1, A_3, B_2, C_4} \\
            \bc{A_2, B_4, C_3, A_3, B_1, C_2} \\
            \bc{A_1, B_3, C_4} \\
            \bc{A_1, B_4, C_2} \\
            \bc{A_2, B_1, C_4} \\
            \bc{A_2, B_2, C_2} \\
            \bc{A_3, B_3, C_3} \\
            \bc{A_3, B_4, C_1} \\
            \bc{A_4, B_1, C_3} \\
            \bc{A_4, B_2, C_1}
        \end{gathered}
        \qquad
        \begin{gathered}
            \textbf{Ancestral Independences} \\
            \bc{A_1, B_1, C_1} \ancestralindep \bc{A_4, B_4, C_4} \\
            \bc{A_1, B_2, C_3} \ancestralindep \bc{A_4, B_3, C_2} \\
            \bc{A_2, B_3, C_1} \ancestralindep \bc{A_3, B_2, C_4} \\
            \bc{A_2, B_4, C_3} \ancestralindep \bc{A_3, B_1, C_2} \\
            \bc{A_1} \ancestralindep \bc{B_3} \ancestralindep \bc{C_4} \\
            \bc{A_1} \ancestralindep \bc{B_4} \ancestralindep \bc{C_2} \\
            \bc{A_2} \ancestralindep \bc{B_1} \ancestralindep \bc{C_4} \\
            \bc{A_2} \ancestralindep \bc{B_2} \ancestralindep \bc{C_2} \\
            \bc{A_3} \ancestralindep \bc{B_3} \ancestralindep \bc{C_3} \\
            \bc{A_3} \ancestralindep \bc{B_4} \ancestralindep \bc{C_1} \\
            \bc{A_4} \ancestralindep \bc{B_1} \ancestralindep \bc{C_3} \\
            \bc{A_4} \ancestralindep \bc{B_2} \ancestralindep \bc{C_1}
        \end{gathered}
    \end{equation*}
    Analogously to the Wagon-Wheel inflation, these pre-injectable sets form a marginal scenario $\mscenario$ which defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{6} + 8 \cdot 4^3 = 16,896$ rows, $\abs{\Events{\jointvar}} = 4^{12} = 16,777,216$ columns and $201,326,592$ non-zero entires.

@@

    For the Triangle structure in particular, the variable permutation group is simply the set of permutations on $A, B, C$: $\Phi\br{\mscenario} = \Perm{A, B, C}$. For the Web inflation (\cref{fig:the_web_inflation}), we have obtained $\gp\br{\PreInj[\graph]{\graph'}}$ which is an order $48$ group with the following $4$ generators:
    \begin{equation*}
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_1 \\
    A_1 &\to A_4 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_1 \\B_1 &\to B_4 \\B_2 &\to B_3 \\B_3 &\to B_2 \\B_4 &\to B_1 \\C_1 &\to C_4 \\C_2 &\to C_3 \\C_3 &\to C_2 \\C_4 &\to C_1
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_2 \\
    A_1 &\to A_1 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_4 \\B_1 &\to C_1 \\B_2 &\to C_3 \\B_3 &\to C_2 \\B_4 &\to C_4 \\C_1 &\to B_1 \\C_2 &\to B_3 \\C_3 &\to B_2 \\C_4 &\to B_4
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_3 \\
    A_1 &\to C_1 \\A_2 &\to C_2 \\A_3 &\to C_3 \\A_4 &\to C_4 \\B_1 &\to A_1 \\B_2 &\to A_2 \\B_3 &\to A_3 \\B_4 &\to A_4 \\C_1 &\to B_1 \\C_2 &\to B_2 \\C_3 &\to B_3 \\C_4 &\to B_4
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_4 \\
    A_1 &\to A_1 \\A_2 &\to A_2 \\A_3 &\to A_3 \\A_4 &\to A_4 \\B_1 &\to B_2 \\B_2 &\to B_1 \\B_3 &\to B_4 \\B_4 &\to B_3 \\C_1 &\to C_3 \\C_2 &\to C_4 \\C_3 &\to C_1 \\C_4 &\to C_2
    \end{aligned}
    \end{equation*}
    % ((3, 2, 1, 0, 7, 6, 5, 4, 11, 10, 9, 8),
    %  (0, 2, 1, 3, 8, 10, 9, 11, 4, 6, 5, 7),
    %  (8, 9, 10, 11, 0, 1, 2, 3, 4, 5, 6, 7),
    %  (0, 1, 2, 3, 5, 4, 7, 6, 10, 11, 8, 9))
    It is easy to verify that $\varphi_1, \varphi_2, \varphi_3, \varphi_4$ are all automorphisms of the web inflation. Moreover they stabilize the pre-injectable sets of \cref{eq:pre_injectable_triangle_structure_web}. Importantly,
    \[ \gp\br{\PreInj[\graph]{\graph'}} \sim \Perm{A,B,C} \]
    To see this, $\varphi_1$ and $\varphi_4$ become the identity element in $\Perm{A,B,C}$ upon removal of the copy-index, leaving $\varphi_2$ to generate reflections and $\varphi_3$ to generate rotations.

>>>>

    Not all sets $N' \subseteq \nodes'$ can be written as the disjoint union of injectable sets, but those that \textit{can} are called the \term{ai-expressible sets} of $\graph'$. A set $N' \subseteq \nodes'$ is a ai-expressible set if it can be decomposed into the disjoint union of injectable sets $N' = \coprod_{i} N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ and all pairs $N_i', N_j'$ are ancestrally independent: $\forall i, j : N_i' \ancestralindep N_j'$.

    A ai-expressible set $N'$ is of primal importance to the Inflation Technique because any distribution over $N'$ will factorize according to its ancestral independence conditions~\cite{Pearl_2009}\footnote{In~\cite{Inflation}, this concept is generalized into terms which can be factorized via d-separation conditions and the corresponding inflated sets are termed \textit{expressible sets}. This generalization was not required for this work in particular because the ancestral independence relations formed a generating set of d-separation conditions for all of the inflations considered in \cref{fig:inflations}.},
    \[ \prob[N'] = \prob[\coprod_i N'_i] = \prod_{i}\prob[N'_i] \]
    Application of the inflation lemma to linear inequalities constraining ai-expressible distributions $\prob[N']$ transforms those inequalities into polynomial inequalities over the injectable distributions, allowing one to replace all terms with probability distributions defined over variables in $\nodes$. Throughout the body of this work, we let $\AI[\graph]{\graph'}$ denote the set of all ai-expressible sets. To derive inequalities for the inflated causal structure $\graph'$, the ai-expressible sets define a marginal scenario $\mscenario$\footnote{Analogously for a marginal scenario $\mscenario$, the ai-expressible sets $\AI[\graph]{\graph'}$ form an \textit{abstract simplicial complex}. Therefore, in practice, it is completely sufficient to focus on the maximal ai-expressible sets.} that are used to derive inequalities using methods discussed in \cref{sec:marginal_satisfiability}.

@@

    \Cref{sec:inflation_technique_main_summary} explains how the Inflation Technique~\cite{Inflation} was used to derive novel causal compatibility inequalities for the Triangle structure by constructing inflations of the Triangle structure satisfying \cref{eq:inflation_defn}. Explicitly, for a given inflation $\graph'$ of the Triangle structure, one constructs a marginal problem (see \cref{sec:marginal_satisfiability}) for the marginal scenario $\mscenario$ composed of the maximal ai-expressible sets of $\graph'$, i.e. $\mscenario = \AI[\graph]{\graph'}$. This section acts as a reference for the particular inflations of the Triangle structure that are mentioned throughout this manuscript. Contained within this section is a depiction of each of these inflations in \cref{fig:inflations} as well as a their ai-expressible sets. An efficient algorithm for computing the injectable and ai-expressible sets of an inflation can be found in~\cite{Inflation}.
    \begin{center}
    \begin{figure}
    \begin{subfigure}[b]{.45\linewidth}
    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure_cut}}
    \caption{The Cut inflation.}\label{fig:cut_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.45\linewidth}
    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral}}
    \caption{The Spiral inflation.}\label{fig:spiral_inflation}
    \end{subfigure}

@@

    The first inequality presented in \cref{sec:found_inequalities} was \cref{eq:ww_ineq}. \cref{eq:ww_ineq} was derived using the Wagon-Wheel inflation in \cref{fig:wagon_wheel_inflation}. The Wagon-Wheel inflation possesses $4$ copies of $C$ ($C_1, C_2, C_3, C_4$) and $2$ copies of $A$ ($A_1, A_2$) and $B$ ($B_1, B_2$) arranged in the shape of a Wagon-Wheel. The maximal ai-expressible sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{eq:pre_injectable_triangle_structure_wagon_wheel}. These maximal ai-expressible sets define the following marginal scenario where the joint variables $\jointvar$ are simply the set of observable nodes in the Wagon-Wheel inflation $\jointvar = \nodes'_O$:
    \[ \mscenario = \AI[\graph]{\graph'} = \bc{\bc{A_2, B_1, C_3, C_1}, \bc{A_1, B_1, C_4, C_2}, \bc{A_1, B_2, C_1, C_3}, \bc{A_2, B_2, C_2, C_4}} \eq \label{eq:wagon_wheel_marginal_model}\]
    Given that the Fritz distribution is defined over $4$-outcomes variables, the variables in the marginal scenario are assigned $4$-outcomes as well. This marginal scenario $\mscenario$ then defines an incidence matrix $M$ capable of accommodating the Fritz distribution that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{4} = 1024$ rows and $\abs{\Events{\jointvar}} = 4^8 = 65,536$ columns. Understandably, this matrix is not reproduced here. The sheer size of the incidence matrix used here makes complete solutions of the marginal problem using tools such as linear-quantifier elimination intractable.

    \begin{equation*}
        \eq \label{eq:pre_injectable_triangle_structure_wagon_wheel}
        \begin{gathered}
            \textbf{Maximal AI-Expressible Sets} \\
            \bc{A_2, B_1, C_3, C_1} \\
            \bc{A_1, B_1, C_4, C_2} \\
            \bc{A_1, B_2, C_1, C_3} \\
            \bc{A_2, B_2, C_2, C_4} \\
        \end{gathered}
        \qquad
        \begin{gathered}
            \textbf{Ancestral Independences} \\
            \bc{A_2, B_1, C_3} \ancestralindep \bc{C_1} \\
            \bc{A_1, B_1, C_4} \ancestralindep \bc{C_2} \\
            \bc{A_1, B_2, C_1} \ancestralindep \bc{C_3} \\
            \bc{A_2, B_2, C_2} \ancestralindep \bc{C_4} \\
        \end{gathered}
    \end{equation*}
    To construct the marginal distribution vector $\probvec^{\mscenario}$ for the Fritz distribution, one begins with $\probvec^{\mscenario}$ defined in a \textit{symbolic} form,
    \[ {\probvec^{\mscenario}}^{\intercal} = \underbrace{\br{\prob[A_2B_1C_3C_1]\br{0000}, \ldots, \prob[A_1B_1C_4C_2]\br{3232}, \ldots, \prob[A_2B_2C_2C_4]\br{3333}}}_{1024 \text{ entries}} \eq \label{eq:marginal_vector_wagon_wheel} \]
    Which can be factored into the ancestrally independent injectable sets using \cref{eq:pre_injectable_triangle_structure_wagon_wheel},
    \[ {\probvec^{\mscenario}}^{\intercal} = \br{\prob[A_2B_1C_3]\br{000}\prob[C_1]\br{0}, \ldots, \prob[A_1B_1C_4]\br{323}\prob[C_2]\br{2}, \ldots, \prob[A_2B_2C_2]\br{333}\prob[C_4]\br{3}} \eq \label{eq:marginal_vector_wagon_wheel_factors}\]
    And penultimately, each probability distribution in \cref{eq:marginal_vector_wagon_wheel_factors} is deflated by dropping copy-indices.
    \[ {\probvec^{\mscenario}}^{\intercal} = \br{\prob[ABC]\br{000}\prob[C]\br{0}, \ldots, \prob[ABC]\br{323}\prob[C]\br{2}, \ldots, \prob[ABC]\br{333}\prob[C]\br{3}} \eq \label{eq:marginal_vector_wagon_wheel_factors_dropped}\]
    This step is permitted because all of the remaining distributions in \cref{eq:marginal_vector_wagon_wheel_factors} are defined over the injectable sets of the Wagon-Wheel inflation. Finally, each of the elements of $\probvec^{\mscenario}$ are replaced with numerical values pursuant to the Fritz distribution. For example, $\prob[ABC]\br{323}\prob[C]\br{2}$ is assigned the following numerical value:
    \[ \prob[ABC]\br{323}\prob[C]\br{2} = \f{1}{32}\br{2 + \sqrt{2}} \cdot \f{1}{4} \simeq 0.0267  \]
    The same is applied to all other entries of $\probvec^{\mscenario}$. Finally, this numerical version of $\probvec^{\mscenario}$ and $M$ are subjected to linear programing software and an infeasibility certificate $y$ was obtained, corresponding precisely to \cref{eq:ww_ineq} using \cref{eq:marginal_vector_wagon_wheel_factors_dropped}.

    The remaining inequalities in \cref{sec:found_inequalities} were derived using the Web inflation of \cref{fig:the_web_inflation}. The maximal ai-expressible sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{eq:pre_injectable_triangle_structure_web}.
    \begin{equation*}
        \eq \label{eq:pre_injectable_triangle_structure_web}
        \begin{gathered}
            \textbf{Maximal AI-Expressible Sets} \\
            \bc{A_1, B_1, C_1, A_4, B_4, C_4} \\
            \bc{A_1, B_2, C_3, A_4, B_3, C_2} \\
            \bc{A_2, B_3, C_1, A_3, B_2, C_4} \\
            \bc{A_2, B_4, C_3, A_3, B_1, C_2} \\
            \bc{A_1, B_3, C_4} \\
            \bc{A_1, B_4, C_2} \\
            \bc{A_2, B_1, C_4} \\
            \bc{A_2, B_2, C_2} \\
            \bc{A_3, B_3, C_3} \\
            \bc{A_3, B_4, C_1} \\
            \bc{A_4, B_1, C_3} \\
            \bc{A_4, B_2, C_1}
        \end{gathered}
        \qquad
        \begin{gathered}
            \textbf{Ancestral Independences} \\
            \bc{A_1, B_1, C_1} \ancestralindep \bc{A_4, B_4, C_4} \\
            \bc{A_1, B_2, C_3} \ancestralindep \bc{A_4, B_3, C_2} \\
            \bc{A_2, B_3, C_1} \ancestralindep \bc{A_3, B_2, C_4} \\
            \bc{A_2, B_4, C_3} \ancestralindep \bc{A_3, B_1, C_2} \\
            \bc{A_1} \ancestralindep \bc{B_3} \ancestralindep \bc{C_4} \\
            \bc{A_1} \ancestralindep \bc{B_4} \ancestralindep \bc{C_2} \\
            \bc{A_2} \ancestralindep \bc{B_1} \ancestralindep \bc{C_4} \\
            \bc{A_2} \ancestralindep \bc{B_2} \ancestralindep \bc{C_2} \\
            \bc{A_3} \ancestralindep \bc{B_3} \ancestralindep \bc{C_3} \\
            \bc{A_3} \ancestralindep \bc{B_4} \ancestralindep \bc{C_1} \\
            \bc{A_4} \ancestralindep \bc{B_1} \ancestralindep \bc{C_3} \\
            \bc{A_4} \ancestralindep \bc{B_2} \ancestralindep \bc{C_1}
        \end{gathered}
    \end{equation*}
    Analogously to the Wagon-Wheel inflation, these ai-expressible sets form a marginal scenario $\mscenario$ which defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{6} + 8 \cdot 4^3 = 16,896$ rows, $\abs{\Events{\jointvar}} = 4^{12} = 16,777,216$ columns and $201,326,592$ non-zero entires.

@@

    For the Triangle structure in particular, the variable permutation group is simply the set of permutations on $A, B, C$: $\Phi\br{\mscenario} = \Perm{A, B, C}$. For the Web inflation (\cref{fig:the_web_inflation}), we have obtained $\gp\br{\AI[\graph]{\graph'}}$ which is an order $48$ group with the following $4$ generators:
    \begin{equation*}
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_1 \\
    A_1 &\to A_4 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_1 \\B_1 &\to B_4 \\B_2 &\to B_3 \\B_3 &\to B_2 \\B_4 &\to B_1 \\C_1 &\to C_4 \\C_2 &\to C_3 \\C_3 &\to C_2 \\C_4 &\to C_1
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_2 \\
    A_1 &\to A_1 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_4 \\B_1 &\to C_1 \\B_2 &\to C_3 \\B_3 &\to C_2 \\B_4 &\to C_4 \\C_1 &\to B_1 \\C_2 &\to B_3 \\C_3 &\to B_2 \\C_4 &\to B_4
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_3 \\
    A_1 &\to C_1 \\A_2 &\to C_2 \\A_3 &\to C_3 \\A_4 &\to C_4 \\B_1 &\to A_1 \\B_2 &\to A_2 \\B_3 &\to A_3 \\B_4 &\to A_4 \\C_1 &\to B_1 \\C_2 &\to B_2 \\C_3 &\to B_3 \\C_4 &\to B_4
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_4 \\
    A_1 &\to A_1 \\A_2 &\to A_2 \\A_3 &\to A_3 \\A_4 &\to A_4 \\B_1 &\to B_2 \\B_2 &\to B_1 \\B_3 &\to B_4 \\B_4 &\to B_3 \\C_1 &\to C_3 \\C_2 &\to C_4 \\C_3 &\to C_1 \\C_4 &\to C_2
    \end{aligned}
    \end{equation*}
    % ((3, 2, 1, 0, 7, 6, 5, 4, 11, 10, 9, 8),
    %  (0, 2, 1, 3, 8, 10, 9, 11, 4, 6, 5, 7),
    %  (8, 9, 10, 11, 0, 1, 2, 3, 4, 5, 6, 7),
    %  (0, 1, 2, 3, 5, 4, 7, 6, 10, 11, 8, 9))
    It is easy to verify that $\varphi_1, \varphi_2, \varphi_3, \varphi_4$ are all automorphisms of the web inflation. Moreover they stabilize the ai-expressible sets of \cref{eq:pre_injectable_triangle_structure_web}. Importantly,
    \[ \gp\br{\AI[\graph]{\graph'}} \sim \Perm{A,B,C} \]
    To see this, $\varphi_1$ and $\varphi_4$ become the identity element in $\Perm{A,B,C}$ upon removal of the copy-index, leaving $\varphi_2$ to generate reflections and $\varphi_3$ to generate rotations.
